Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-08 paper_comparison/paper_comparison/paper_comparison.Rmd
mostly finish exp design

Since $z = O(x^j)$, for $j > 1$, $z$ is a higher order term leaves out by the null regression, which will result in model misspecification. Visual patterns of non-linearity were simulated using four different order of probabilist's Hermite polynomials ($j = 2, 3, 6, 18$) and four different distribution of $X_{raw}$: (1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$.

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", NA),
           sigma = c("0.25", "1", "2", "4", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1", "4", "16", "64"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "cccccc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Summary of factors involved in the study.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "Standard deviation of polynomial model\n(sym3)",
                                 "Orientation of heteroskedasticity\n(sym4)", 
                                 "Variance factor of heteroskedasticity model\n(sym5)",
                                 "Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

@@

For $b \neq 0$, the variance-covariance matrix of the error term $\boldsymbol{\varepsilon}$ is correlated with the regressor $x$, which will lead to the presence of heteroskedasticity. Visual patterns were simulated using three different shapes ($a$ = -1, 0, 1) and the same four different distribution of $X_{raw}$ used in experiment I.

@@

As summarised by Table \ref{tab:model-factor-table}, three additional parameters $n$, $\sigma$ and $b$ were used to control the strength of the signal so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ were used in experiment I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters.

@@

```{r different-n, fig.cap="Three different values of $n$ are used in experiment I, II and III to control the strength of the signal."}
ori_dat <- poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1.5)$gen(300)

@@

patchwork::wrap_plots(p2, p3, p1, ncol = 2)
```

```{r different-sigma, fig.cap="Example residual plots of the linear regression model used in experiment I. Four different values of $\\sigma$ are included in the experiment to control the strength of the signal."}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

@@

patchwork::wrap_plots(p1, p2, p3, p4, ncol = 2)
```

```{r different-b, fig.cap="Example residual plots of the linear regression model used in experiment II. Five different values of $b$ are included in the experiment to control the strength of the signal."}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

@@

patchwork::wrap_plots(p1, p2, p3, p4, p5, ncol = 3)
```

@@

Three replications are made for each of the parameter values shown in Table \ref{tab:parameter-table} resulting in 1152 different lineups. In addition, each lineup is designed to be evaluated by five different subjects and lineups with uniform distribution is designed to be evaluated by 11 subjects to provide reasonable estimates of the visual p-value.

Thus, $443$ subjects were recruited to satisfy the design of the experiment. 
<!-- TODO:subject allocation algorithm -->

@@

Subjects for all three experiments were recruited from an crowdsourcing platform called Prolific [ref here]. Prescreening procedure was applied during the recruitment, subjects were required to be fluent in English, with $98\%$ minimum approval rate in other studies and 10 minimum submissions. During the experiment, every subject was presented with a block of 20 lineups. For each lineup, the actual data plot was drawn as a standard residual plot of the null model with raw residuals on the y-axis and fitted values on the x-axis. An additional horizontal red line was added at $y = 0$ as a helping line. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The lineup consisted of 20 residual plots with one randomly placed actual data plot. And for every lineup, the subject was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots were from others. If there was no noticeable difference between plots in a lineup, subjects were permitted to select zero plots without providing the reason. No subject was shown the same lineup twice. Information about preferred pronoun, age group, education, and previous experience in visual experiment were also collected. In every block of 20 lineups that presented to a subject, two lineups with obvious visual patterns were included as attention checks. A subject's submission was only accepted if the actual data plot was identified for at least one attention check. Data of rejected submissions were discarded automatically to maintain the overall data quality.

>>>>

Since $z = O(x^j)$, for $j > 1$, $z$ is a higher order term leaves out by the null regression, which will result in model misspecification. Visual patterns of non-linearity were simulated using four different order of probabilist's Hermite polynomials ($j = 2, 3, 6, 18$) and four different distribution of $X_{raw}$: (1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$. A summary of the factors is given in Table \ref{tab:model-factor-table}.

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", "NA"),
           sigma = c("0.25", "1", "2", "4", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1", "4", "16", "64"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "cccccc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Summary of factors involved in the study.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "Standard deviation of polynomial model\n(sym3)",
                                 "Shape of heteroskedasticity\n(sym4)", 
                                 "Variance factor of heteroskedasticity model\n(sym5)",
                                 "Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

@@

For $b \neq 0$, the variance-covariance matrix of the error term $\boldsymbol{\varepsilon}$ is correlated with the regressor $x$, which will lead to the presence of heteroskedasticity. Visual patterns were simulated using three different shapes ($a$ = -1, 0, 1) and the same four different distribution of $X_{raw}$ used in experiment I. A summary of the factors is given in Table \ref{tab:model-factor-table}.

@@

As summarised in Table \ref{tab:model-factor-table}, three additional parameters $n$, $\sigma$ and $b$ were used to control the strength of the signal so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ were used in experiment I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters. A large value of $\sigma$ will increase the variation of the error of the polynomial model and decrease the visibility of the visual pattern. The parameter $b$ controls the ratio of the standard deviation of the heteroskedasticity across the domain of the regressor. Given $x \neq a$, a larger value of $b$ will lead to a larger ratio of the variance at $x$ to the variance at $x - a = 0$, making the visual pattern more obvious.

@@

```{r different-n, fig.height = 3, fig.cap="Three different values of $n$ are used in experiment I, II and III to control the strength of the signal."}
ori_dat <- poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1.5)$gen(300)

@@

patchwork::wrap_plots(p2, p3, p1, ncol = 3)
```

```{r different-sigma, fig.height = 2, fig.cap="Example residual plots of the linear regression model used in experiment I. Four different values of $\\sigma$ are included in the experiment to control the strength of the signal."}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

@@

```{r different-b, fig.height = 2, fig.cap="Example residual plots of the linear regression model used in experiment II. Five different values of $b$ are included in the experiment to control the strength of the signal."}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

@@

patchwork::wrap_plots(p1, p2, p3, p4, p5, ncol = 5)
```

@@

Three replications are made for each of the parameter values shown in Table \ref{tab:parameter-table} resulting in $(4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = 1116$ different lineups. In addition, each lineup is designed to be evaluated by five different subjects. After attempting some pilot studies internally in our research group, we decide to present a block of 20 lineups to every subject. And to ensure the quality of the survey data, two lineups with obvious visual patterns are included as attention checks. Thus, $576 \times 5/(20-2) = 160$ and $540 \times 5 /(20-2) = 150$ subjects were recruited to satisfy the design of the experiment I and experiment II respectively.

As mentioned in Section [the alpha section], $\alpha$ used in Equation \ref{eq:eq:pvalue-beta-binomial} needs to be estimated using Rorschach lineups. Hence, 36 Rorschach lineups with all combinations of $n$ and $X_{raw}$ and three replications are designed to be included in experiment III. All Rorschach lineups are planned to be evaluated by 20 subjects. However, presenting only Rorschach lineups to subjects are considered to be bad practices as subjects will lose interest quickly. We planned to also collect 6 more evaluations on the 279 lineups with uniform distribution, resulted in $(36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3)/(20-2) = 133$ subjects recruited for experiment III.

<!-- TODO:subject allocation algorithm -->

@@

Subjects for all three experiments were recruited from an crowdsourcing platform called Prolific [ref here]. Prescreening procedure was applied during the recruitment, subjects were required to be fluent in English, with $98\%$ minimum approval rate in other studies and 10 minimum submissions. During the experiment, every subject was presented with a block of 20 lineups. For each lineup, the actual data plot was drawn as a standard residual plot of the null model with raw residuals on the y-axis and fitted values on the x-axis. An additional horizontal red line was added at $y = 0$ as a helping line. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The lineup consisted of 20 residual plots with one randomly placed actual data plot. And for every lineup, the subject was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots were from others. If there was no noticeable difference between plots in a lineup, subjects were permitted to select zero plots without providing the reason. No subject was shown the same lineup twice. Information about preferred pronoun, age group, education, and previous experience in visual experiment were also collected. A subject's submission was only accepted if the actual data plot was identified for at least one attention check. Data of rejected submissions were discarded automatically to maintain the overall data quality.

### 2022-10-08 paper_comparison/paper_comparison/paper_comparison.tex
mostly finish exp design

Since \(z = O(x^j)\), for \(j > 1\), \(z\) is a higher order term leaves
out by the null regression, which will result in model misspecification.
Visual patterns of non-linearity were simulated using four different
order of probabilist's Hermite polynomials (\(j = 2, 3, 6, 18\)) and
four different distribution of \(X_{raw}\): (1) \(U(-1, 1)\), (2)
\(N(0, 0.3^2)\), (3) \(lognormal(0, 0.6^2)/3\) and (4) \(u\{1, 5\}\).

@@

\caption{\label{tab:model-factor-table}Summary of factors involved in the study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{1}{c}{\makecell[c]{Order of Hermite polynomial\\($j$)}} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{\makecell[c]{Standard deviation of polynomial model\\($\sigma$)}} & \multicolumn{1}{c}{\makecell[c]{Orientation of heteroskedasticity\\($a$)}} & \multicolumn{1}{c}{\makecell[c]{Variance factor of heteroskedasticity model\\($b$)}} & \multicolumn{1}{c}{\makecell[c]{Sample size\\($n$)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1 & 0 & 1 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2 & 1 & 4 & 300\\
18 & $U\{1, 5\}$ & 4 &  & 16 & \\
 & NA &  &  & 64 & \\
\bottomrule
\end{tabular}}
\end{table}

@@

For \(b \neq 0\), the variance-covariance matrix of the error term
\(\boldsymbol{\varepsilon}\) is correlated with the regressor \(x\),
which will lead to the presence of heteroskedasticity. Visual patterns
were simulated using three different shapes (\(a\) = -1, 0, 1) and the
same four different distribution of \(X_{raw}\) used in experiment I.

@@

As summarised by Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters.

@@

Three replications are made for each of the parameter values shown in
Table \ref{tab:parameter-table} resulting in 1152 different lineups. In
addition, each lineup is designed to be evaluated by five different
subjects and lineups with uniform distribution is designed to be
evaluated by 11 subjects to provide reasonable estimates of the visual
p-value.

Thus, \(443\) subjects were recruited to satisfy the design of the
experiment.

@@

Subjects for all three experiments were recruited from an crowdsourcing
platform called Prolific {[}ref here{]}. Prescreening procedure was
applied during the recruitment, subjects were required to be fluent in
English, with \(98\%\) minimum approval rate in other studies and 10
minimum submissions. During the experiment, every subject was presented
with a block of 20 lineups. For each lineup, the actual data plot was
drawn as a standard residual plot of the null model with raw residuals
on the y-axis and fitted values on the x-axis. An additional horizontal
red line was added at \(y = 0\) as a helping line. The 19 null datasets
were generated by the residual rotation technique, and plotted in the
same way. The lineup consisted of 20 residual plots with one randomly
placed actual data plot. And for every lineup, the subject was asked to
select one or more plots that are most different from others, provide a
reason for their selections, and evaluate how different they think the
selected plots were from others. If there was no noticeable difference
between plots in a lineup, subjects were permitted to select zero plots
without providing the reason. No subject was shown the same lineup
twice. Information about preferred pronoun, age group, education, and
previous experience in visual experiment were also collected. In every
block of 20 lineups that presented to a subject, two lineups with
obvious visual patterns were included as attention checks. A subject's
submission was only accepted if the actual data plot was identified for
at least one attention check. Data of rejected submissions were
discarded automatically to maintain the overall data quality.

>>>>

Since \(z = O(x^j)\), for \(j > 1\), \(z\) is a higher order term leaves
out by the null regression, which will result in model misspecification.
Visual patterns of non-linearity were simulated using four different
order of probabilist's Hermite polynomials (\(j = 2, 3, 6, 18\)) and
four different distribution of \(X_{raw}\): (1) \(U(-1, 1)\), (2)
\(N(0, 0.3^2)\), (3) \(lognormal(0, 0.6^2)/3\) and (4) \(u\{1, 5\}\). A
summary of the factors is given in Table \ref{tab:model-factor-table}.

@@

\caption{\label{tab:model-factor-table}Summary of factors involved in the study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{1}{c}{\makecell[c]{Order of Hermite polynomial\\($j$)}} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{\makecell[c]{Standard deviation of polynomial model\\($\sigma$)}} & \multicolumn{1}{c}{\makecell[c]{Shape of heteroskedasticity\\($a$)}} & \multicolumn{1}{c}{\makecell[c]{Variance factor of heteroskedasticity model\\($b$)}} & \multicolumn{1}{c}{\makecell[c]{Sample size\\($n$)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1 & 0 & 1 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2 & 1 & 4 & 300\\
18 & $U\{1, 5\}$ & 4 &  & 16 & \\
 & NA &  &  & 64 & \\
\bottomrule
\end{tabular}}
\end{table}

@@

For \(b \neq 0\), the variance-covariance matrix of the error term
\(\boldsymbol{\varepsilon}\) is correlated with the regressor \(x\),
which will lead to the presence of heteroskedasticity. Visual patterns
were simulated using three different shapes (\(a\) = -1, 0, 1) and the
same four different distribution of \(X_{raw}\) used in experiment I. A
summary of the factors is given in Table \ref{tab:model-factor-table}.

@@

As summarised in Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters. A large value of
\(\sigma\) will increase the variation of the error of the polynomial
model and decrease the visibility of the visual pattern. The parameter
\(b\) controls the ratio of the standard deviation of the
heteroskedasticity across the domain of the regressor. Given
\(x \neq a\), a larger value of \(b\) will lead to a larger ratio of the
variance at \(x\) to the variance at \(x - a = 0\), making the visual
pattern more obvious.

@@

Three replications are made for each of the parameter values shown in
Table \ref{tab:parameter-table} resulting in
\((4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = 1116\)
different lineups. In addition, each lineup is designed to be evaluated
by five different subjects. After attempting some pilot studies
internally in our research group, we decide to present a block of 20
lineups to every subject. And to ensure the quality of the survey data,
two lineups with obvious visual patterns are included as attention
checks. Thus, \(576 \times 5/(20-2) = 160\) and
\(540 \times 5 /(20-2) = 150\) subjects were recruited to satisfy the
design of the experiment I and experiment II respectively.

As mentioned in Section {[}the alpha section{]}, \(\alpha\) used in
Equation \ref{eq:eq:pvalue-beta-binomial} needs to be estimated using
Rorschach lineups. Hence, 36 Rorschach lineups with all combinations of
\(n\) and \(X_{raw}\) and three replications are designed to be included
in experiment III. All Rorschach lineups are planned to be evaluated by
20 subjects. However, presenting only Rorschach lineups to subjects are
considered to be bad practices as subjects will lose interest quickly.
We planned to also collect 6 more evaluations on the 279 lineups with
uniform distribution, resulted in
\((36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3)/(20-2) = 133\)
subjects recruited for experiment III.

@@

Subjects for all three experiments were recruited from an crowdsourcing
platform called Prolific {[}ref here{]}. Prescreening procedure was
applied during the recruitment, subjects were required to be fluent in
English, with \(98\%\) minimum approval rate in other studies and 10
minimum submissions. During the experiment, every subject was presented
with a block of 20 lineups. For each lineup, the actual data plot was
drawn as a standard residual plot of the null model with raw residuals
on the y-axis and fitted values on the x-axis. An additional horizontal
red line was added at \(y = 0\) as a helping line. The 19 null datasets
were generated by the residual rotation technique, and plotted in the
same way. The lineup consisted of 20 residual plots with one randomly
placed actual data plot. And for every lineup, the subject was asked to
select one or more plots that are most different from others, provide a
reason for their selections, and evaluate how different they think the
selected plots were from others. If there was no noticeable difference
between plots in a lineup, subjects were permitted to select zero plots
without providing the reason. No subject was shown the same lineup
twice. Information about preferred pronoun, age group, education, and
previous experience in visual experiment were also collected. A
subject's submission was only accepted if the actual data plot was
identified for at least one attention check. Data of rejected
submissions were discarded automatically to maintain the overall data
quality.
